%Roll number 22 Chinmay Gireesh
\textbf{\textcolor{LightMagenta}{Define Hidden Markov Model. (May 2019) \hfill 4 marks}} \\[5pt]
In Hidden Markov Model, (HMM), the states are not observable, but when we
visit a state, an observation is recorded.Hidden Markov models (HMMs) are a formal foundation for making probabilistic models of linear sequence ’labeling’ problems 1 , 2 . They
provide a conceptual toolkit for building complex models just by drawing an intuitive picture. They are at the heart of a diverse range of programs, including gene finding, profile
searches, multiple sequence alignment and regulatory site identification. HMMs are the Legos of computational sequence analysis.\\
Because of their flexibility and computational efficiency, hidden Markov models have found
a wide application in many different fields. They are known for their use in temporal pattern
recognition and generation such as speech recognition, handwriting recognition, and speech
synthesis.\\
Hidden Markov models evolve according to two rules:
\begin{enumerate}
    \item The first rule is that the model moves from the current state to the next state, which
may be the same state, according to some probability distribution that depends only on the
current state. This is known as the Markov property. Intuitively, this rule states that the
system evolves without regard to past states of the system and only depends on the current
state.
\item The second rule is that after each transition, the model emits an observation whose distribution depends only on the current state. Since the model only emits the observations and
the states generating the observations are unknown to the observer, the states generating
those observations are called hidden states.
\end{enumerate}
