%Roll number 19 Benedict Benny 
\textbf{\textcolor{LightMagenta}{List any four applications of Machine Learning.(May 2019) \\. \hfill4 marks}} \\[5pt]
Machine learning is one of the most exciting technologies that one would have
ever come across. As it is evident from the name, it gives the computer that which makes it
more similar to humans: The ability to learn. Machine learning is actively being used today,
perhaps in many more places than one would expect. We probably use a learning algorithm
dozens of time without even knowing it. Applications of Machine Learning include:
\begin{enumerate}
\item \textcolor{purple}{\underline{\smash{Web Search Engine}}:}One of the reasons why search engines like google, bing etc work
so well is because the system has learnt how to rank pages through a complex learning
algorithm.
\item \textcolor{purple}{\underline{\smash{Photo tagging Applications}}:} Be it Facebook or any other photo tagging application,
the ability to tag friends makes it even more happening. It is all possible because of a face
recognition algorithm that runs behind the application.
\item \textcolor{purple}{\underline{\smash{Spam Detector}}:}Our mail agent like Gmail or Hotmail does a lot of hard work for us
in classifying the mails and moving the spam mails to spam folder. This is again achieved
by a spam classifier running in the back end of mail application.
\item \textcolor{purple}{\underline{\smash{Traffic Alerts(Maps)}}:} Everyone using maps is providing their location, average speed,
the route in which they are traveling which in turn helps Google collect massive Data about
the traffic, which makes them predict the upcoming traffic and adjust your route according
to it.
\end{enumerate}