% Roll number 4, Adersh G R

\textbf{\textcolor{LightMagenta}{Compare k means clustering with hierarchical clustering
techniques? (September 2020, Qn 10) \hfill 4 marks}} \\[5pt]
\textcolor{purple}{k-means Clustering} \\
k-means, using a pre-specified number of clusters, the method assigns records to each
cluster to find the mutually exclusive cluster of spherical shape based on distance. It
needs advance knowledge of K i.e. no. of clusters one want to divide your data. We can
use the median or mean as a cluster centre to represent each cluster. In K Means
clustering, since one starts with a random choice of clusters, the results produced by
running the algorithm many times may differ. It also found to work well when the
structure of the clusters is hyperspherical (like a circle in 2D, the sphere in 3D). The
main advantage of K means clustering is that Convergence is guaranteed. In k-means
Clustering, K-Value is difficult to predict. Also, it won’t work well with a global cluster.

\textcolor{purple}{Hierarchical Clustering}
\\
In hierarchical clustering we can stop at any number of clusters, we can find appropriate
by interpreting the dendrogram. Hierarchical methods can be either divisive or
agglomerative. Agglomerative methods begin with ‘n’ clusters and sequentially combine
similar clusters until only one cluster is obtained. Divisive methods work in the opposite
direction, beginning with one cluster that includes all the records and Hierarchical
methods are especially useful when the target is to arrange the clusters into a natural
hierarchy. Results are reproducible in Hierarchical clustering. Hierarchical clustering is a
set of nested clusters that are arranged as a tree.Hierarchical clustering doesn’t work as
well as, k means when the shape of the clusters is hyperspherical. Main advantages of
hierarchial clustering is the Ease of handling of any forms of similarity or distance.
Disadvantage is that Hierarchical clustering requires the computation and storage of an
n×n distance matrix. For very large datasets, this can be expensive and slow 1.