% Roll number 47, Neil

\textbf{\textcolor{LightMagenta}{Discuss any four Examples of machine learning models?(September 2020: Qno 11b) \hfill 4 marks}} \\[5pt]
\begin{enumerate}
    \item   
    \textcolor{purple}{Supervised Learning} \\
    Supervised learningis the machine learning task of learning a function that maps an
    input to an output based on example input-output pairs. It infers a function from
    labelled training data consisting of a set of training examples In supervised learning,
    each example is a pair consisting of an input object (typically a vector) and the
    desired output value (also called the supervisory signal). A supervised learning
    algorithm analyzes the training data and produces an inferred function, which can be
    used for mapping new examples. An optimal scenario will allow for the algorithm to
    correctly determine the class labels for unseen instances. 
    
    \item 
    \textcolor{purple}{Decision tree} \\
    A decision tree is a flowchart like structure in which each internal node represents a
    "test" on an attribute (e.g. whether a coin flip comes up heads or tails), each branch
    represents the outcome of the test, and each leaf node represents a class label
    (decision taken after computing all attributes). The paths from root to leaf represent
    classification rules.In decision analysis, a decision tree and the closely related influence
    diagram are used as a visual and analytical decision support tool, where the expected
    values (or expected utility) of competing alternatives are calculated.
    
    \\
    A decision tree consists of three types of nodes:\\
    \begin{itemize}
        \item Decision nodes – typically represented by squares
        \item Chance nodes – typically represented by circles
        \item End nodes – typically represented by triangles
    \end{itemize}
    
    \item 
    \textcolor{purple}{Random forests or random decision forests} \\
    classification, regression and other tasks that operate by constructing a multitude of
    decision trees at training time and outputting the class that is the mode of the classes
    (classification) or mean/average prediction (regression) of the individual trees.Random
    decision forests correct for decision trees' habit of overfitting to their training set.
    Random forests generally outperform decision trees, but their accuracy is lower than
    gradient boosted trees. However, data characteristics can affect their performance.\\
    
    \item 
    \textcolor{purple}{Neural Networks}
    \\
    A neural network is a series of algorithms that endeavours to recognize
    underlying relationships in a set of data through a process that mimics the way
    the human brain operates. In this sense, neural networks refer to systems of
    neurons, either organic or artificial in nature. Neural networks can adapt to
    changing input; so the network generates the best possible result without
    needing to redesign the output criteria. The concept of neural networks, which
    has its roots in artificial intelligence, is swiftly gaining popularity in the
    development of trading systems.
\end{enumerate}